### 2018-12-04 Sections/cloud_quantum_computing.tex
more indexing

Perhaps the simplest illustrative example is to consider the execution of a Monte Carlo simulation\index{Monte-Carlo simulations}. Here we wish to execute a large number of instances of the same problem, each with a different random seed, and average the results to yield a statistical outcome. Here the \textsc{Map} algorithm simply delegates out $k$ copies of the same algorithm, assigning each node a different random seed\index{Random seed}, and the \textsc{Reduce} algorithm needs only average their outputs. Note that the \textsc{Map} and \textsc{Reduce} algorithms are relatively simple, with the nodes operating in parallel doing all the hardcore number crunching.

@@

The availability of a globe-spanning quantum satellite network brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite communication} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

>>>>

Perhaps the simplest illustrative example is to consider the execution of a Monte Carlo simulation\index{Monte-Carlo simulations}. Here we wish to execute a large number of instances of the same problem, each with a different random seed, and average the results to yield a statistical outcome. Here the \textsc{Map} algorithm simply delegates out $k$ copies of the same algorithm, assigning each node a different random seed\index{Random!Seed}, and the \textsc{Reduce} algorithm needs only average their outputs. Note that the \textsc{Map} and \textsc{Reduce} algorithms are relatively simple, with the nodes operating in parallel doing all the hardcore number crunching.

@@

The availability of a globe-spanning quantum satellite network brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellites!Satellite-to-satellite communication} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

### 2018-12-04 Sections/essay_to_the_future_QKD.tex
more indexing

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellite-to-ground communication}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Private-key} for private-key cryptography\index{Private-key!Cryptography} with guaranteed key secrecy.

>>>>

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellites!Satellite-to-ground communication}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Private-key} for private-key cryptography\index{Private-key!Cryptography} with guaranteed key secrecy.

### 2018-12-04 Sections/models_for_quantum_computation.tex
indexing
more indexing

\subsection{Circuit model} \label{sec:circuit_model} \index{Circuit model}

@@

The first is to use the ideas of \textit{micro-clusters}\index{Micro-cluster states} and cluster state recycling\index{Cluster states!Recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walks}, which is biased in the direction of state growth. This approach is discussed in more detail in Secs.~\ref{sec:CS_LO} \& \ref{sec:module}.

>>>>

\subsection{Circuit model} \label{sec:circuit_model} \index{Circuit!Model}

@@

The first is to use the ideas of \textit{micro-clusters}\index{Micro-cluster states} and cluster state recycling\index{Cluster states!Recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random!Walks}, which is biased in the direction of state growth. This approach is discussed in more detail in Secs.~\ref{sec:CS_LO} \& \ref{sec:module}.

### 2018-12-04 Sections/network_topologies.tex
more indexing

\subsubsection{Random tree} \index{Random tree topologies}

@@

\subsection{Random}\index{Random topologies}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}\index{Random topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (left to right).} \label{fig:random_graph}\index{Random topologies}
	\end{figure*}
\fi

>>>>

\subsubsection{Random tree} \index{Random!Tree topologies}

@@

\subsection{Random}\index{Random!Topologies}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}\\
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}\index{Random!Topologies}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{random_0}
	\includegraphics[clip=true, width=0.325\textwidth]{random_05}
	\includegraphics[clip=true, width=0.325\textwidth]{random_1}
	\captionspacefig \caption{The 15-vertex random graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (left to right).} \label{fig:random_graph}\index{Random!Topologies}
	\end{figure*}
\fi

### 2018-12-04 Sections/physical_architectures_for_quantum_computing.tex
more indexing

We then define a strategy, $\mathcal{S}$\index{Fusion!Strategies}, for choosing clusters we have stored and bonding them together to form larger clusters. The strategy acts on our cluster vector and updates it accordingly,
\begin{align}\index{Update rules}
\vec{n}_{t+1} = \mathcal{S}(\vec{n}_t).
\end{align}
That is, the length vector can be thought of as a series of `buckets' containing clusters of different lengths, and the strategy simply probabilistically shuffles the contents of the buckets around each time it is applied. The process can be thought of as a random walk\index{Random walks}, guided by a probabilistic update rule. Fig.~\ref{fig:linear_cs_strategy} outlines the protocol.

@@

Let us describe the operation of a parity measurement\index{Parity measurements} (i.e Bell analyser) device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily extend to other non-trivial operations, such as CNOT and CZ gates or QND measurements\index{Quantum non-demolition measurements}.

>>>>

We then define a strategy, $\mathcal{S}$\index{Fusion!Strategies}, for choosing clusters we have stored and bonding them together to form larger clusters. The strategy acts on our cluster vector and updates it accordingly,
\begin{align}\index{Update rules}
\vec{n}_{t+1} = \mathcal{S}(\vec{n}_t).
\end{align}
That is, the length vector can be thought of as a series of `buckets' containing clusters of different lengths, and the strategy simply probabilistically shuffles the contents of the buckets around each time it is applied. The process can be thought of as a random walk\index{Random!Walks}, guided by a probabilistic update rule. Fig.~\ref{fig:linear_cs_strategy} outlines the protocol.

@@

Let us describe the operation of a parity measurement\index{Parity measurements} (i.e Bell analyser) device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily extend to other non-trivial operations, such as CNOT and CZ gates or QND measurements\index{Quantum non-demolition measurements (QND)}.

### 2018-12-04 Sections/protocols_for_the_quantum_internet.tex
more indexing

\subsection{Quantum non-demolition measurement}\index{Quantum non-demolition measurement (QND)}

@@

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket\psi} & \ctrl{1} & \qw & \hat{M}\ket\psi \\
    \lstick{\ket{0}} & \targ & \qw & \meter \\
} \nonumber
\end{align}
\captionspacefig \caption{Quantum non-demolition measurement of a single qubit. $\hat{M}$ is the measurement operator applied during measurement to the ancillary state, which may be destructive. The primary qubit has now been projected onto the measurement outcome $\hat{M}$, but has not been destroyed.}\index{Quantum non-demolition measurement (QND).}\label{fig:QND_circ}
\end{figure}

@@

\subsection{Random number generation} \index{Random number generation}

@@

For cryptographic purposes , there are far more stringent constraints placed upon our random number generator than for use in say a Monte-Carlo computer simulation -- cryptographic random number generation\index{Cryptographic!Random number generation}. In this context, the demands placed upon the amount of bias or correlations in the random number stream are very stringent. An enormous amount of research has been invested into this topic, and sophisticated statistical tests have been developed for establishing crypto-worthiness of a random number stream. The fact that quantum random numbers, via the inherent non-determinism of quantum mechanics, do not obey any hidden variable theory, implies there is intrinsically no underlying `seed'\index{Random seed} to the random number stream, which reveals the entire deterministic sequence. This is unlike any classical generator, where there always is such a seed, but it is simply taken to be too hard to determine.

>>>>

\subsection{Quantum non-demolition measurement}\index{Quantum non-demolition measurements (QND)}

@@

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket\psi} & \ctrl{1} & \qw & \hat{M}\ket\psi \\
    \lstick{\ket{0}} & \targ & \qw & \meter \\
} \nonumber
\end{align}
\captionspacefig \caption{Quantum non-demolition measurement of a single qubit. $\hat{M}$ is the measurement operator applied during measurement to the ancillary state, which may be destructive. The primary qubit has now been projected onto the measurement outcome $\hat{M}$, but has not been destroyed.}\index{Quantum non-demolition measurements (QND)}\label{fig:QND_circ}
\end{figure}

@@

\subsection{Random number generation} \index{Random!Number generation}

@@

For cryptographic purposes , there are far more stringent constraints placed upon our random number generator than for use in say a Monte-Carlo computer simulation -- cryptographic random number generation\index{Cryptographic!Random number generation}. In this context, the demands placed upon the amount of bias or correlations in the random number stream are very stringent. An enormous amount of research has been invested into this topic, and sophisticated statistical tests have been developed for establishing crypto-worthiness of a random number stream. The fact that quantum random numbers, via the inherent non-determinism of quantum mechanics, do not obey any hidden variable theory, implies there is intrinsically no underlying `seed'\index{Random!Seed} to the random number stream, which reveals the entire deterministic sequence. This is unlike any classical generator, where there always is such a seed, but it is simply taken to be too hard to determine.

### 2018-12-04 Sections/the_quantum_space_race.tex
more indexing

Involving ground-based quantum network nodes is not an inherent problem as 80\% of the atmosphere by mass is located within the first 12km in altitude, yielding low effective thickness of the atmosphere ($\sim10$km)\index{Effective atmospheric thickness}. This effective thickness of course changes with the azimuth of the satellite in the sky. Near the horizon the line-of-sight\index{Line-of-sight} between satellite and ground-station is far greater than when the satellite is directly overhead. The light trajectory beyond this effective thickness regime effectively passes through vacuum with attenuation\index{Photon loss} limited only by diffraction\index{Diffraction}. Thus, when directly overhead, a satellite-to-ground\index{Satellite-to-ground communication} channel is more favourable in terms of signal attenuation than long-distance ground-to-ground\index{Ground-to-ground communication} channels.

Ground-to-satellite\index{Ground-to-satellite communication} and satellite-to-ground\index{Satellite-to-ground communication} quantum communication have already been demonstrated, as will be discussed in detail in the next section. Such a satellite-based quantum communication system is naturally suited to various tasks, in particular QKD\index{Quantum key distribution (QKD)}, which does not require quantum memories\index{Quantum memory} or impose onerous timing constraints. However, with the addition of quantum memories the capabilities of such a quantum network could be greatly enhanced, enabling many of the applications and protocols described earlier (Part.~\ref{part:protocols}) at a global scale.

@@

There are two main ingredients for communication in a global satellite-based quantum internet: satellite-to-satellite\index{Satellite-to-satellite communication}, and ground-to-satellite\index{Ground-to-satellite communication}, shown in Fig.~\ref{fig:space_1}. Each bring with them their own engineering challenges.

@@

A third experiment performed QKD in a satellite-to-ground\index{Satellite-to-ground communication} configuration, where the ground station was at Xinglong \cite{bib:liao2017satellite}. The protocol that was used was the decoy-state BB84\index{Decoy states}\index{BB84 protocol} protocol, which is robust against a photon-number splitting attack\index{Photon-number-splitting attacks}. A key-rate of between $1-12$kbit/s was achieved while the satellite was visible, depending upon the relative location in the sky, shown in Fig.~\ref{fig:space_4}(d).

@@

Initial results indicated polarisation preservation of photons emitted from the satellite, a preliminary step towards performing protocols such as BB84\index{BB84 protocol} \cite{bib:carrasco2016leo}. More recent results showed quantum-limited satellite-to-ground\index{Satellite-to-ground communication} communication was possible, attaining a quantum bit error rate below 5\% \cite{bib:takenaka2017} during the closest approach of the satellite to the ground at a distance of 744km. The downlink was established over distances of over 1,000km, although for obvious reasons the error rate was higher for longer distances.

@@

From the point of view of security, we anticipate that initial quantum networks for QKD will be based on trusted nodes\index{Trusted nodes}. Due to the inherent practical difficulty of tampering with space-based trusted nodes, it is likely this will offer a sufficient level of practical security for most realistic applications. Thus, using a constellation of satellites employing QKD can achieve long-distance cryptography by simply relaying the information, either by multiple satellite-to-ground\index{Satellite-to-ground communication} or satellite-to-satellite\index{Satellite-to-satellite communication} configurations. For ultimate security, not relying on the use of trusted nodes, one would employ alternative protocols that do not require line-of-sight quantum communication, such as the E91 protocol \cite{bib:PRL_67_661}\index{E91 protocol}. As this requires entanglement distribution, storage, and purification\index{Entanglement!Purification}, this would most likely be a second-generation technology after the trusted node QKD network is fully established and successfully demonstrated.

>>>>

Involving ground-based quantum network nodes is not an inherent problem as 80\% of the atmosphere by mass is located within the first 12km in altitude, yielding low effective thickness of the atmosphere ($\sim10$km)\index{Effective atmospheric thickness}. This effective thickness of course changes with the azimuth of the satellite in the sky. Near the horizon the line-of-sight\index{Line-of-sight} between satellite and ground-station is far greater than when the satellite is directly overhead. The light trajectory beyond this effective thickness regime effectively passes through vacuum with attenuation\index{Photon loss} limited only by diffraction\index{Diffraction}. Thus, when directly overhead, a satellite-to-ground\index{Satellites!Satellite-to-ground communication} channel is more favourable in terms of signal attenuation than long-distance ground-to-ground\index{Ground-to-ground communication} channels.

Ground-to-satellite\index{Ground-to-satellite communication} and satellite-to-ground\index{Satellites!Satellite-to-ground communication} quantum communication have already been demonstrated, as will be discussed in detail in the next section. Such a satellite-based quantum communication system is naturally suited to various tasks, in particular QKD\index{Quantum key distribution (QKD)}, which does not require quantum memories\index{Quantum memory} or impose onerous timing constraints. However, with the addition of quantum memories the capabilities of such a quantum network could be greatly enhanced, enabling many of the applications and protocols described earlier (Part.~\ref{part:protocols}) at a global scale.

@@

There are two main ingredients for communication in a global satellite-based quantum internet: satellite-to-satellite\index{Satellites!Satellite-to-satellite communication}, and ground-to-satellite\index{Ground-to-satellite communication}, shown in Fig.~\ref{fig:space_1}. Each bring with them their own engineering challenges.

@@

A third experiment performed QKD in a satellite-to-ground\index{Satellites!Satellite-to-ground communication} configuration, where the ground station was at Xinglong \cite{bib:liao2017satellite}. The protocol that was used was the decoy-state BB84\index{Decoy states}\index{BB84 protocol} protocol, which is robust against a photon-number splitting attack\index{Photon-number-splitting attacks}. A key-rate of between $1-12$kbit/s was achieved while the satellite was visible, depending upon the relative location in the sky, shown in Fig.~\ref{fig:space_4}(d).

@@

Initial results indicated polarisation preservation of photons emitted from the satellite, a preliminary step towards performing protocols such as BB84\index{BB84 protocol} \cite{bib:carrasco2016leo}. More recent results showed quantum-limited satellite-to-ground\index{Satellites!Satellite-to-ground communication} communication was possible, attaining a quantum bit error rate below 5\% \cite{bib:takenaka2017} during the closest approach of the satellite to the ground at a distance of 744km. The downlink was established over distances of over 1,000km, although for obvious reasons the error rate was higher for longer distances.

@@

From the point of view of security, we anticipate that initial quantum networks for QKD will be based on trusted nodes\index{Trusted nodes}. Due to the inherent practical difficulty of tampering with space-based trusted nodes, it is likely this will offer a sufficient level of practical security for most realistic applications. Thus, using a constellation of satellites employing QKD can achieve long-distance cryptography by simply relaying the information, either by multiple satellite-to-ground\index{Satellites!Satellite-to-ground communication} or satellite-to-satellite\index{Satellites!Satellite-to-satellite communication} configurations. For ultimate security, not relying on the use of trusted nodes, one would employ alternative protocols that do not require line-of-sight quantum communication, such as the E91 protocol \cite{bib:PRL_67_661}\index{E91 protocol}. As this requires entanglement distribution, storage, and purification\index{Entanglement!Purification}, this would most likely be a second-generation technology after the trusted node QKD network is fully established and successfully demonstrated.
